\begin{chineseabstract}
    {浙江传媒学院，毕业论文，\hologo{LaTeX}模板，全文的浓缩}本文是浙江传媒学院本
    科毕业论文模板cuzthesis的使用说明文档。主要内容为介绍\hologo{LaTeX}文档类
    cuzthesis的用法，以及撰写毕业论文的一些拙见。

    \begin{leftbar}
        \noindent\textbf{建议：}摘要是全文的浓缩，要涵盖文章的主要内容，一般应保
        证字数在300以上，须包括如下三点：做了什么、如何做的、做得怎样。具体而
        言：\textbf{第一段}，可以用一句话概述课题背景；接着再用一两句话表明做的
        东西。\textbf{第二段}，可以用三五句话描述如何做的，包括做这个东西分几步
        （或几个模块），每步（模块）的任务，以及相邻步（或相关模块）之间的关系。
        \textbf{最后一段}，用两三句话概括作品的亮点，以及效果怎样，包括可能的市
        场反响、用户体验等等。
        
        \noindent{}需要注意的是，既然是全文的浓缩，就不要出现类似“本项目将要做
        到”或者“详情见正文”等此类语句，因其并非正文中应出现的说法（既然已经是正
        文的浓缩，再说详情见正文就产生了矛盾）。此外，语言上应注意言简意赅，语气
        上应平实无感。
    \end{leftbar}
\end{chineseabstract}
\begin{englishabstract}
    {Communication University of Zhejiang (CUZ), thesis, \LaTeX{} Template,
    abstraction of the whole thesis} This documentation is a helper for the
    \LaTeX{} class \texttt{cuzthesis}, which is a thesis template for the
    Communication University of Zhejiang. The main content is about how to use
    the \texttt{cuzthesis}, as well as some advices of writing thesis.

    \begin{leftbar}
        \noindent\textbf{Suggestions:} Abstract is the abstraction of the whole
        thesis, which should cover the main aspects of the thesis, and should
        contain no less than 300 words, involving 3 aspects: what is done, how
        to do it, and what about the result. Specifically, \textbf{1st
        paragraph}, introduce the background by 1 sentence, and what is done by
        1 or 2 sentence(s). \textbf{2nd paragraph}, describe how to do it by 3
        to 5 sentences, including how many steps (modules) are used, what each
        step (module) does, and the relationship between adjacent steps (related
        modules). \textbf{Last paragraph}, extract the most important features
        of the work and its effect by 2 or 3 sentences, including possible
        responses of markets, user experiences, etc..
    	
    	\noindent Note that, since it is the abstraction of the whole thesis,
    	expressions such as ``this project will'' or ``readers are refered to
    	the body of thesis for details'' should be avoided, for this saying
    	should not appear in the body of thesis (now that this is the
    	abstraction, a refering to the body of thesis generates a conflict).
    	Besides, the language should be neat, and the tone should be plain and
    	without emotions.
    \end{leftbar}
\end{englishabstract}